The Overlapping Control Volume Finite Element Method for Multiphase Porous Media Flow Modelling \\ Part I: Numerical Formulation

### 2015-01-18 Papers/Prototype_1_Method/article_figure1.tex
updates
updates in paper 1: trasnfering content on the BL test case from paper 2 to paper 1

\begin{figure}[htp]
\begin{center}
\hbox{\hspace{-2.5cm}
\includegraphics[width=1.2\textwidth]{diagrams/overlapping}}
\caption{An isometric schematic of the 2D overlapping velocity
  elements. In this example we show a triangular element, ABD in the
  $x$-$y$ plane. We also indicate the contol volume boundaries lying
  within this element. Under the overlapping methodology presented
  here, each facet formed from the union of control volume and element
  possesses its own polynomial representation for velocity, indicated
  by height in the isometric projection. By extrapolating this
  representation across the rest of this element, we negate the need
  to implement a special data structure to store or evaluate this
  field, instead leveraging the standard finite element basis for ABD,
  and storing the FEM nodal values E, F, G. }
\label{fig:overlapping2d}
\end{center}
\end{figure}

@@

\begin{comment}
%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
%\vbox{
\includegraphics[width=15.5cm,height=12.cm]{./diagrams/Fields_Plume.pdf}
%\includegraphics[width=15.5cm,height=12.cm]{./diagrams/AllHighRes.pdf}
%\vspace{-1.5cm}
%\includegraphics[width=12.5cm,height=9.cm]{./diagrams/AllHighRes.pdf}}
%\vspace{1.cm}
\caption{Advection problem test-cases: Comparison of the resulting 2D advected field after 100 time-steps using continuous and discontinuous (between elements) formulations, in which (2): element size of 0.05 ($\sim$46 elements) and (3): element size: 0.10 ($\sim$ 11 elements).\label{2D_Sanpshot_Adv2D}}
%P$_{1}$DG-P$_{2}$, P$_{2}$DG-P$_{2}$ and P$_{1}$DG-P$_{1}$DG finite elements. There are 11.5k nodes within 22.5k elements. \label{2D_Sanpshot_Adv2D}}
%\caption{Advection problem test-cases: Comparison of the resulting 2D advected field at $t = 0.5$ (500 time-steps) for P$_{1}$DG-P$_{2}$, P$_{2}$DG-P$_{2}$ and P$_{1}$DG-P$_{1}$DG finite elements. There are 11.5k nodes within 22.5k elements. \label{2D_Sanpshot_Adv2D}}
\end{center}
\end{figure}
\end{comment}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\vbox{\vspace{-1.5cm}\hbox{
\includegraphics[width=15.5cm,height=10.cm]{./diagrams/Step_P1DG-P2Cont}}
\vspace{-.5cm}
\hbox{
\includegraphics[width=15.5cm,height=10.cm]{./diagrams/Plume_P1DG-P2Cont}}}\vspace{-1cm}
\caption{Advection problem test-cases: Comparison of the resulting 2D advected field after 350 (top: step function) and 100 (bottom: Gaussian plume function) time-steps (high-resolution mesh as reference case for time-step size) using continuous and discontinuous (between elements) formulations. Mesh grids used in these simulations are described in Table~\ref{table:meshplume}.\label{2D_Sanpshot_Adv2D}}
%P$_{1}$DG-P$_{2}$, P$_{2}$DG-P$_{2}$ and P$_{1}$DG-P$_{1}$DG finite elements. There are 11.5k nodes within 22.5k elements. \label{2D_Sanpshot_Adv2D}}
%\caption{Advection problem test-cases: Comparison of the resulting 2D advected field at $t = 0.5$ (500 time-steps) for P$_{1}$DG-P$_{2}$, P$_{2}$DG-P$_{2}$ and P$_{1}$DG-P$_{1}$DG finite elements. There are 11.5k nodes within 22.5k elements. \label{2D_Sanpshot_Adv2D}}
\end{center}
\end{figure}

@@

\begin{comment}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=14.5cm,height=13.5cm]{./diagrams/AllNorms.png}
%\begin{center}
%\vbox{
%\includegraphics[width=12.5cm,height=9.5cm]{./diagrams/All_L1_PlumeConvergence.png}
%\vspace{-3.cm}
%\includegraphics[width=12.5cm,height=9.5cm]{./diagrams/All_L2_PlumeConvergence.png}}
%\vspace{2.cm}
\caption{Advection problem test-cases: comparison of convergence, $L_{1}$ and $L_{2}$ norms for 2D solutions obtained from continuous and discontinuous (between elements) formulations. \label{L1_L2norm_Adv2D}}
%\caption{Advection problem test-cases: comparison of convergence, $L_{1}$ (top) and $L_{2}$ norms for 2D solutions obtained with $\left(\text{P}_{1}\text{DG-P}_{2}\right.$ and $\left.\text{P}_{2}\text{DG-P}_{2}\right)$ and without $\left(\text{P}_{1}\text{DG-P}_{1}\text{DG}\right)$ discontinuity between elements. \label{L1_L2norm_Adv2D}}
\end{center}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.\textwidth]{diagrams/bl-exact-meth-upwind.eps}
\end{center}
\caption{Buckley--Leverett test-cases: Saturation solutions for the
  continuous upwind method for different 1D P$_{1}$DG-P$_{2}$ mesh
  resolutions and comparison against standard analytical solution.
\label{bl-exact-meth-upwind}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
  %\begin{center}
\vbox{\hbox{\hspace{2.5cm}
    \includegraphics[width=0.62\textwidth]{diagrams/BL_1d_P0DGP1_convergence.eps}}
\vspace{-.0cm}\hbox{\hspace{2.5cm}
    \includegraphics[width=0.62\textwidth]{diagrams/BL_1d_P1DGP2_convergence.eps}}
\vspace{-.0cm}\hbox{\hspace{2.5cm}
    \includegraphics[width=0.62\textwidth]{diagrams/BL_1d_P2DGP3_convergence.eps}}}
   % \includegraphics[width=0.45\textwidth]{BL_2d_P1DGP2_convergence}
    \caption{Buckley--Leverett test-cases: Saturation profiles for a
      number of element-pairs and numerical resolutions in 1D --
      P$_{0}$DG-P$_{1}$ (top), P$_{1}$DG-P$_{2}$ and P$_{2}$DG-P$_{3}$
      (bottom).\label{fig:BL_profiles}}
  %\end{center}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{\hbox{\hspace{1.cm}
    \includegraphics[width=0.8\textwidth]{diagrams/L1_convergence_rate.eps}}
\vspace{.0cm}\hbox{\hspace{1.cm}
    \includegraphics[width=0.8\textwidth]{diagrams/L2_convergence_rate.eps}}}
    \caption{Buckley--Leverett test-cases: L1 (top) and L2 (bottom)
      error convergence rates for a number of element
      pairs. \label{fig:BL_converg-rates}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.\textwidth]{diagrams/bl-upwind-v-up-and-down.eps}
\end{center}
\caption{Buckley--Leverett test-cases: Comparison of the optimal
  upwind formulation when using upwinding (OU) and coupled
  upwind/downwind (OU-D). The finite element interpolation of the
  saturation field $\left(S_{1}\right)$ is shown at different mesh
  resolutions. Downwind seems to detract from the accuracy of the
  solution. \label{bl-upwind-v-up-and-down}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\begin{center}
\includegraphics[width=1.\textwidth]{diagrams/bl-exact-meth-cv-0-8-ele50.eps}
\end{center}
\vspace{0.cm}}
\caption{Buckley--Leverett test-cases: Comparison of control volume
  solutions using 80$\%$ upwinding and with optimal upwinding and
  using 50 continuous P$_{1}$DG-P$_{2}$
  elements. \label{bl-exact-meth-cv-0-8-ele50}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.\textwidth]{diagrams/bl-dg-2eles.eps}
\end{center}
\caption{Buckley--Leverett test-cases: Two element solution using the
  discontinuous formulation. Saturation field from both CV solution
  and FEM interpolation are shown.  \label{bl-dg-2eles}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-20.eps}}
\vspace{-0.cm}
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-cent-4-10-20.eps}}}
\caption{Buckley--Leverett test-cases: Saturation field obtained from
  the discontinuous and continuous formulation with different mesh
  resolutions. Solutions with (top) and without (bottom) upwinding
  scheme. Notice that oscillations are suppressed with the upwinding
  scheme.\label{bl-dg-cent-4-10-20}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-vers-cty.eps}}
\vspace{-0.cm}
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-p1-2-4-5-10-20-40.eps}}}
\caption{Buckley--Leverett test-cases: Saturation field obtained from
  (top) continuous and discontinuous (between elements) formulations
  (solution with 50 elements may be considered as a converged
  result). Solution obtained (bottom) from linear pressure (P1)
  formulation with different mesh resolution with comparison against
  P2-pressure formulation (continuous). \label{bl-dg-4-10-vers-cty}}
\end{figure}

\begin{figure}[H]
\vbox{
\begin{center}
\includegraphics[width=17.5cm,height=12.5cm]{diagrams/bl-dg-4-10-vers-cty}
\end{center}
\vspace{0.cm}}
\caption{Gas saturations shown comparing the accuracy of the
  discontinuous between elements and continuous formulation. The 50
  element continuous solution may be viewed as a converged result.  }
\label{bl-dg-4-10-vers-cty}
\end{figure}

\end{comment}

%%%
%%%  FIGURE 
%%%

%%%
%%%  FIGURE 
%%%

>>>>

\begin{figure}[htp]
\begin{center}
\hbox{\hspace{-3.7cm}
\includegraphics[width=1.4\textwidth]{diagrams/overlapping}}
\caption{An isometric schematic of the 2D overlapping velocity
  elements. In this example we show a triangular element, ABD in the
  $x$-$y$ plane. We also indicate the contol volume boundaries lying
  within this element. Under the overlapping methodology presented
  here, each facet formed from the union of control volume and element
  possesses its own polynomial representation for velocity, indicated
  by height in the isometric projection. By extrapolating this
  representation across the rest of this element, we negate the need
  to implement a special data structure to store or evaluate this
  field, instead leveraging the standard finite element basis for ABD,
  and storing the FEM nodal values E, F, G. }
\label{fig:overlapping2d}
\end{center}
\end{figure}

@@

%%%            %%%
%%%  COMMENTS  %%%
%%%            %%%
\begin{comment}
%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
%\vbox{
\includegraphics[width=15.5cm,height=12.cm]{./diagrams/Fields_Plume.pdf}
%\includegraphics[width=15.5cm,height=12.cm]{./diagrams/AllHighRes.pdf}
%\vspace{-1.5cm}
%\includegraphics[width=12.5cm,height=9.cm]{./diagrams/AllHighRes.pdf}}
%\vspace{1.cm}
\caption{Advection problem test-cases: Comparison of the resulting 2D advected field after 100 time-steps using continuous and discontinuous (between elements) formulations, in which (2): element size of 0.05 ($\sim$46 elements) and (3): element size: 0.10 ($\sim$ 11 elements).\label{2D_Sanpshot_Adv2D}}
%P$_{1}$DG-P$_{2}$, P$_{2}$DG-P$_{2}$ and P$_{1}$DG-P$_{1}$DG finite elements. There are 11.5k nodes within 22.5k elements. \label{2D_Sanpshot_Adv2D}}
%\caption{Advection problem test-cases: Comparison of the resulting 2D advected field at $t = 0.5$ (500 time-steps) for P$_{1}$DG-P$_{2}$, P$_{2}$DG-P$_{2}$ and P$_{1}$DG-P$_{1}$DG finite elements. There are 11.5k nodes within 22.5k elements. \label{2D_Sanpshot_Adv2D}}
\end{center}
\end{figure}
\end{comment}
%%%            %%%
%%%  COMMENTS  %%%
%%%            %%%

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\vbox{\vspace{-2.cm}\hbox{
\includegraphics[width=15.5cm,height=10.cm]{./diagrams/Step_P1DG-P2Cont}}
\vspace{-.5cm}
\hbox{
\includegraphics[width=15.5cm,height=10.cm]{./diagrams/Plume_P1DG-P2Cont}}}\vspace{-1cm}
\caption{Advection problem test-cases: Comparison of the resulting 2D advected field after 350 (top: step function) and 100 (bottom: Gaussian plume function) time-steps (high-resolution mesh as reference case for time-step size) using continuous and discontinuous (between elements) formulations. Mesh grids used in these simulations are described in Table~\ref{table:meshplume}.\label{2D_Sanpshot_Adv2D}}
%P$_{1}$DG-P$_{2}$, P$_{2}$DG-P$_{2}$ and P$_{1}$DG-P$_{1}$DG finite elements. There are 11.5k nodes within 22.5k elements. \label{2D_Sanpshot_Adv2D}}
%\caption{Advection problem test-cases: Comparison of the resulting 2D advected field at $t = 0.5$ (500 time-steps) for P$_{1}$DG-P$_{2}$, P$_{2}$DG-P$_{2}$ and P$_{1}$DG-P$_{1}$DG finite elements. There are 11.5k nodes within 22.5k elements. \label{2D_Sanpshot_Adv2D}}
\end{center}
\end{figure}

@@

%%%            %%%
%%%  COMMENTS  %%%
%%%            %%%
\begin{comment}
%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=14.5cm,height=13.5cm]{./diagrams/AllNorms.png}
%\begin{center}
%\vbox{
%\includegraphics[width=12.5cm,height=9.5cm]{./diagrams/All_L1_PlumeConvergence.png}
%\vspace{-3.cm}
%\includegraphics[width=12.5cm,height=9.5cm]{./diagrams/All_L2_PlumeConvergence.png}}
%\vspace{2.cm}
\caption{Advection problem test-cases: comparison of convergence, $L_{1}$ and $L_{2}$ norms for 2D solutions obtained from continuous and discontinuous (between elements) formulations. \label{L1_L2norm_Adv2D}}
%\caption{Advection problem test-cases: comparison of convergence, $L_{1}$ (top) and $L_{2}$ norms for 2D solutions obtained with $\left(\text{P}_{1}\text{DG-P}_{2}\right.$ and $\left.\text{P}_{2}\text{DG-P}_{2}\right)$ and without $\left(\text{P}_{1}\text{DG-P}_{1}\text{DG}\right)$ discontinuity between elements. \label{L1_L2norm_Adv2D}}
\end{center}
\end{figure}

\end{comment}
%%%            %%%
%%%  COMMENTS  %%%
%%%            %%%
